%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Mike Moore} % Your name
\address{19200 Space Center Blvd Apt \#2034 \\ Houston, TX 77058} % Your address
\address{(832)~$\cdot$~338~$\cdot$~3475 \\ michael.moore@nasa.gov} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Texas, Austin} \hfill {\em Dec 2010} \\ 
B.S. in Aerospace Engineering \\
GPA: 3.32

{\bf University of Houston Clear Lake} \hfill {\em On going} \\ 
Graduate Courses in Computer Engineering \\
GPA: 3.75

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{L3 Stratis}{January 2010 - Present}{Software Modeling and Simulation Engineer}{NASA Johnson Space Center (JSC) - Houston, TX}
\item Modeling and simulation developer working within JSC ER-7. This is the branch within JSC's
Engineering and Robotics division that is responsible for software and simulation.
\item Currently part of a team of eight to ten engineers who develop complete space vehicle simulations in order to model and evaluate proposed vehicle designs intended for NASA deep space and Mars missions.
\item Lead the team's power, thermal, and life support system modeling efforts.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{University of Texas Center for Space Research}{June 2010 - December 2010}{Student Researcher}{Austin, TX}
\item Student research assistant. Helped graduate students and post-docs process and analyze data from 
the pair of GRACE satellites (Gravity Recovery and Climate Experiment). These satellites were a collaboration between NASA and U.T. Austin. They launched in 2002 and are still returning scientific data.
\item Work included writing scripts to process large data sets associated with the performance
of the GRACE satellites' thermal control system, and scientific sensors on-board. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{United Space Alliance}{December 2009 - August 2009}{Navigation and Flight Operations Co-Op}{Houston, TX}
\item Supported the Space Shuttle navigation flight controller operations team as a Co-Op.
\item Built a model and then simulated the Lunar Reconnaissance Orbiter's planned trajectory in order to investigate the application of Kalman Filters and batch processing techniques for lunar spacecraft navigation.
\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Dynamical Systems Modeling & Thermal, Electrical, Fluidic, and Control system modeling. \\
Embedded Hardware & TI TMS320 C2000, TI Code Composer Studio, Arduino\\
Lab Skills & Signal generators, oscilloscopes, logic analyzers, soldering.\\
Programming Languages & C/C++, VHDL, C\#, Java, Python, JavaScript, Matlab \\
Misc Programming Tools & Vi, Visual Studio, Eclipse, Git, SVN, Jenkins, Matlab, LaTeX \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WEB LINKS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Web Links}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Quad Copter Flight Test & https://www.youtube.com/watch?v=c9tHnrJNVy0 \\
Quad Copter 3D Simulation & https://www.youtube.com/watch?v=864sEgLVOQA \\
\end{tabular}

\end{rSection}

\end{document}
